\cvsection{Work Experience}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Uptrust} % Organization
    {} % Location
    {Apr. 2021 - Jun. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented backend requirements for product features necessary for new and expiring contracts - video chat, announcements, recurring events, and multiple-staff associations.}
        \item {Took ownership of the the messaging system services and contributed major enhancements for system reliability and 10x scale.}
        \begin{itemize}
          \item {Introduced queue alerts, retries, backpressure, and rate-limiting for improved observability and resiliency.}
          \item {Migrated queues away from \textbf{Firebase}, and re-wrote data access to use \textbf{GraphQL} and \textbf{Postgres} for improved tail latencies and throughput.}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cvthreeentry
    {Salesforce} % Organization
    {} % Location
    {Senior Software Engineer}
    {Mar. 2017 - Apr. 2021}
    {Intern (Core Search)}
    {Jun. 2016 - Sep. 2016}
    {Intern (Service Cloud)}
    {Jun. 2015 - Sep. 2015}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Worked cross-team to prioritize and perform work necessary to migrate search services to the public cloud architecture, Hyperforce.}
        \begin{itemize}
          \item {Lead the implementation for novel "many \textbf{Kubernetes} namespaces" solution for search team's developer productivity in order to meet strict company timelines - presented this solution to the CTO and principal architects.}
          \item {Deployed critical \textbf{microservices} for search relevancy in the first AWS Hyperforce regions.}
          \item {Designed and implemented performance improvements necessary for the stricter public cloud latency requirements.}
        \end{itemize}
        \item {Designed and implemented p50 and p99 latency improvements in legacy services, necessary for the Instant Results product feature.}
        \item {Implemented key features for \textbf{feature toggling, A/B experimentation}, and the \textbf{gRPC execution engine}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Annai Systems} % Organization
    {} % Location
    {June. 2014 - Sep. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built and tested an encrypted high-speed transport service for genome sequencing with \textbf{OpenSSL} and \textbf{C/C++}.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
